### 2017-04-06 abstract1.tex
...

% \markboth{中~文~摘~要}{中~文~摘~要}
\begin{tabular}{l l}
论文题目：& 基于溯因诊断修复词向量模型的研究\\
专\quad\quad 业：& 软件工程\\
硕\,\,\,士\,\,\,生：& 马华冠\\
指导教师：& 万海\quad 副教授\\
\end{tabular}
\vspace{1cm}
%\chapter*{摘\quad 要}

@@

\centerline{\hei\xiaoerhao 摘\quad 要}
\vspace{0.5cm}
词嵌入是近年来比较热门的一个研究方向，词嵌入的目的是通过低纬度的稠密向量表征出知识库中的实体和关系的语义信息，在有效存储信息的基础上，能够实现实体预测、链接预测等推理任务。目前，大多数的工作集中在通过优化评分函数、损失函数等来训练出一个更有效的翻译模型，使得训练出的翻译模型可以在meanrank、Hit@10的评分标准下取得更好的成绩。本文考虑到翻译模型训练数据与本体语义的相关性，利用本体推理研究的现有成果提出一种新的方法来提升构建出的翻译模型的性能。这种方法使用本体完成对训练集的语义表达，同时使用测试数据中的三元组集合构建出观察值的集合。通过这种方式，本文把优化翻译模型的问题，转化成本体研究中的溯因推理问题。溯因诊断是本体新知识获取的一个重要的推理方法，这种方法可以揭示出观察值没有被成功推理出的根本原因，并且可以提供出与原本体语义一致的解释集。解释集中的公理与本体中的公理具有相同的语法，在使用获得的解释集对缺陷本体进行完善修复后，新的本体不仅可以蕴含观察值，还因为关键性公理的补全，有着更好的获取新知识的能力。
	在本体的溯因诊断中，限制解释集的大小是必须考虑的一个关键因素。解释集过于强大的表达能力会导致解空间的无限膨胀，而过度地压缩解的空间，不仅会极大地削弱解释集的表达能力，也会影响解释集的对缺漏公理的覆盖能力。为了平衡解释集的表达能力与解空间的矛盾，本文根据决断集合的特点提出一个新的概念，决断集合模版。基本地，决断集合模版由决断集中获取，获取方法是把决断集中的公理进行变量化，解释集会从原本体以及决断集模版的集合中进行计算，然后实例化得来。同时，为了限制解释集的空间，本文会介绍一个新的概念，最小决断集模版。利用最小决断集模版 ，我们可以有效地限制解释集的空间大小。 在本体的溯因诊断中，观察值的表达是另外一个需要考虑的因素，但是在词向量模型的训练集的数据中，三元组是它的唯一表达方式，因此本文将会使用简化的表达语言完成对观察值集合的表达，这样可以使得解释集的解空间缩小而不影响解释集的表达能力。
	本文的目标是通过利用本体的表达能力对词嵌入的训练数据进行表达，从而把优化词向量模型的问题转化成本体研究中的溯因诊断问题。通过利用决断集模版的语义能力，我们可以从模版和集合中实例化出目标解释集。然后，利用诊断出来的结果，我们可以对词向量的训练数据进行修正，从而达到优化训练出来的词向量模型的目的。最后，我们还设置了一组相关的实验，验证本文得出的解释集对训练数据的修正能力，以及对比不同方法下所得出的词向量模型的表达能力和推理能力。

\vspace{2cm}
{\bfseries 关键词：本体；词向量；溯因诊断}

>>>>

% \markboth{中~文~摘~要}{中~文~摘~要}
\begin{tabular}{l l}
论文题目：& 基于溯因诊断修复知识库模型的研究\\
专\quad\quad 业：& 软件工程\\
硕\,\,\,士\,\,\,生：& \\
指导教师：& \quad \\
\end{tabular}
\vspace{1cm}
%\chapter*{摘\quad 要}

@@

\centerline{\hei\xiaoerhao 摘\quad 要}
\vspace{0.5cm}
词嵌入是近年来比较热门的一个研究方向，词嵌入的目的是通过低纬度的稠密向量表征出知识库中的实体和关系的语义信息，在有效存储信息的基础上，能够实现实体预测、链接预测等推理任务。目前，大多数的工作集中在通过优化评分函数、损失函数等来训练出一个更有效的翻译模型，使得训练出的翻译模型可以在meanrank、Hit@10的评分标准下取得更好的成绩。然而在现实中经常会出现由于数据集的不完善，导致某些符合客观事实的链接无法被正确的预测。 本文的主要工作，是利用本体中溯因推理的技术找出这些链接无法被正确预测的原因，并计算出合乎语义的解释对数据集进行修复。

	溯因推理是描述逻辑中一项重要的推理机制，它的目的是找到观察值无法被本体蕴含的原因，并提供合乎逻辑的解释。在本体的溯因诊断中，限制解释集的大小是必须考虑的一个关键因素。为了平衡解释集的表达能力与解空间的矛盾，本文根据决断集的特点提出了概念决断集模版。决断集合模版可以决断集中获取，利用决断集模版我们限制了解释的数量。同时，我们还提出了$\subseteq_\mathsf{ds}$-$\emph{minimal}$概念进一步地在保证语义不缺失的情况下减小解释集数量。

	我们的目标是计算所有合理解释，合理的解释需要满足的条件包括可接受，非平凡，一致并且是$\subseteq_\mathsf{ds}$-$\emph{minimal}$的。在本文中，我们提供了完整的算法来计算所有满足条件的解释。最后，我们利用生成的解释来实现对知识库的修复。我们基于本文提出的算法实现了PBA系统，在PBA系统我们测试了解释集对知识库的修复能力。实验结果证明了我们提出的方法具有有效性以及合理性。

\vspace{2cm}
{\bfseries 关键词：本体；决断集；溯因诊断；词嵌入}

### 2017-04-06 abstract2.tex
...

%\thispagestyle{empty} %取消当前页码
%\chapter[ABSTRACT（英文摘要）]{Abstract}
\begin{tabular}{l l}
Title：& Query Answering with Existential Rules Repairs of \\& Inconsistent Ontologies under Stable Model Semantics\\
Major：& Software Engineering\\
Name：& Huaguan Ma\\
Supervisor：& Hai Wan\\
\end{tabular}
\vspace{1cm}
%\chapter*{Abstract}
% \markboth{英~文~摘~要}{英~文~摘~要}
\phantomsection
\addcontentsline{toc}{chapter}{Abstract}

@@

Word embedding is a popular research direction in recent years. The purpose of word embedding is to express the semantic information of entities and relationships in the knowledge base through the dense vector of low latitude. Based on the effective storage of information, it can perform entity prediction, link Prediction and other reasoning tasks. At present, most of the work focuses on training a more efficient translation model by optimizing the scoring function, loss function, etc., so that the trained translation model can achieve better results under the score of meanrank and Hit@10. This paper takes into account the relevance of the translation model training data to the ontology semantics, and puts forward a new method to enhance the performance of the translated model by using the existing results of ontology reasoning research. This method uses the ontology to complete the semantic expression of the training set, and uses the set of triples in the test data to construct a set of observations. In this way, this paper transforms the problem of optimizing the translation model into the problem of abductive reasoning in ontology research. The retrospective diagnosis is an important reasoning method for the acquisition of new knowledge of ontology. This method can reveal the root cause that the observed value has not been successfully entailed, and can provide the explanation which is consistent with the original body semantics. The axiom of the explanation has the same grammar as the axiom in the ontology. After using the obtained explanation to perfect the defect ontology, the new ontology can not only contain the observation value, but also because of the completeness of the key axiom, The ability to acquire new knowledge.
In the ontology diagnosis of the ontology, limiting the size of the explanatory set is a key factor that must be considered. Interpretation of the set of too strong expression will lead to the infinite expansion of the solution space, and excessive compression of the solution space, not only will greatly weaken the interpretation of the set of expression ability, will also affect the interpretation of the lack of coverage of the lack of ability. In order to balance the contradiction between the expression ability of the explanation and the solution space, this paper proposes a new concept based on the characteristics of the decision set. Basically, the decision set template is obtained from the decision, and the acquisition method is to quantify the axioms of the decision set, and the explanation assembly is calculated from the original set and the set of decision sets, and then instantiated. At the same time, in order to limit the space of the interpretation set, this article will introduce a new concept, the smallest template. In the ontology diagnosis of the ontology, the expression of the observation is another factor to consider, but in the data set of the training set of the word vector model, the triplet is its only expression, so this article will use the simplified expression The language completes the expression of the set of observations, which allows the solution space of the interpretation set to be reduced without affecting the expression of the interpretation set.
The goal of this paper is to express the training data of the word by using the expression ability of the ontology, so as to transform the problem of the optimization word vector model into the dying diagnosis problem in the ontology research. By using the semantic capabilities of the decision set template, we can extract the target set from the template and the set of examples. Then, using the results of the diagnosis, we can modify the training data of the word vector so as to achieve the purpose of optimizing the vector model of the training. Finally, we also set up a set of related experiments to verify the corrective ability of the explanatory set to be derived from the training data, and to compare the expression ability and reasoning ability of the word vector model obtained under different methods.

{\bf Key Words:  Ontology; Word Vector; Abduction Diagnosis}
%\clearpage

>>>>

%\thispagestyle{empty} %取消当前页码
%\chapter[ABSTRACT（英文摘要）]{Abstract}
\begin{tabular}{l l}
Title：& Query Answering with Existential Rules Repairs of \\& Inconsistent Ontologies under Stable Model Semantics\\
Major：& Software Engineering\\
Name：& \\
Supervisor：& \\
\end{tabular}
\vspace{1cm}
%\chapter*{Abstract}
% \markboth{英~文~摘~要}{英~文~摘~要}
\phantomsection
\addcontentsline{toc}{chapter}{Abstract}

@@

Word embedding is a popular research direction in recent years. The purpose of word embedding is to express the semantic information of entities and relationships in the knowledge base through the dense vector of low latitude. Based on the effective storage of information, it can realize entity prediction, link Prediction and other reasoning tasks. At present, most of the work focuses on training a more efficient translation model by optimizing the scoring function, loss function, etc., so that the trained translation model can achieve better results under the score of meanrank and Hit@10. However, in reality there are often due to the imperfect data set, resulting in some of the objective facts of the link can not be correctly predicted. The main work of this paper is to use the technique of ontology abduction to find out why these links can not be correctly predicted and to calculate the semantic explanation to repair the data set.

Abductive reasoning is an important reasoning mechanism in describing logic, and its purpose is to find the reasons why observations can not be implied by the ontology and provide logical explanations. In the ontology diagnosis of the ontology, limiting the size of the explanatory set is a key factor that must be considered. In order to balance the contradiction between the expression ability of the interpretation set and the solution space, this paper puts forward the concept jutification pattern according to the characteristics of the justification. Determine the set of templates that can be determined collectively, using the decision set template we limit the number of explanations. At the same time, we also suggest that the $\subseteq_\mathsf{ds}$-$\emph{minimal}$ concept further reduces the number of explanatory sets without guaranteeing that semantics are not missing.

Our goal is to calculate all reasonable explanations, reasonable explanations that need to be met, including acceptable, non-trivial, consistent and is $\subseteq_\mathsf{ds}$-$\emph{minimal}$. In this paper, we provide a complete algorithm to compute all explanations that satisfy the condition. Finally, we use the generated explanation to achieve the repair of the knowledge base. We have implemented the PBA system based on the algorithm proposed in this paper. In the PBA system, we have tested the ability to solve the knowledge base. The experimental results show that the proposed method is effective and reasonable.

{\bf Key Words:  Ontology; Word Embedding; Justification; Abduction Diagnosis}
%\clearpage

### 2017-04-06 chap1.tex
...

	Sutskever, Salakhutdinov, and Tenenbaum(2009)是较早的提出使用贝叶斯聚类网络对关系进行因式分解表达，他们的方法对于每一个实体都使用了超过一个向量进行表达\cite{SS09}\cite{S11}，不过Bordes等人认为对于每个实体都使用多个向量表达难以做到一般化表达。实际上在Bordes随后进行的实验也发现，这种方法构建出来的模型无法轻松地捕获处于稀疏位置的实体\cite{BordesUGWY13}。之后又有多项工作针对性地提高这类知识库模型的性能表现，但是大多数情况下提升有限，或者是应用场景狭窄，无法做到一般化。在自然语言处理领域，嵌入的概念最早由Bengio等人提出，在Bengio等人构建的语言框架模型中所有的单词都会被学习出一个嵌入。随后，Bordes提出了一种新的神经网络架构，这种架构被设计成可以将所有实体和关系嵌入到一个灵活且连续的向量空间。但由于嵌入方式的选择问题，导致构建出的模型性能较为低下。因此在2013年，Bordes根据词向量的特性，将知识库中实体的关系翻译成向量中的平移操作，从而提出了用于将实体嵌入到向量空间的翻译模型TransE\cite{BordesUGWY13}。TransE相比之前的方法，在不仅模型简单，性能提升幅度大，更为关键的是它提出了一种新的思路，给向量模型的构建提出了新的方向。之后的知识表示学习的模型，大多数都是从TransE扩展而来。
\subsection{本体与溯因诊断研究现状}
	利用本体对知识库建模是语义网领域一直备受关注的研究方向。本体的构建方法多样而且复杂，图1.1\cite{OntS01}展示了经典的本体构建流程，在构建本体的过程中，本体与观察值不一致或本体无法蕴含观察值的现象是很常见的\cite{LL13,LDI12}。因此在年来本体的研究热点开始转移到对本体的修复上。溯因推理由于推理方式与人的思考方式具有较高的一致性， 因此溯因推理技术被大量应用在本体的修复任务中。

>>>>

	Sutskever, Salakhutdinov, and Tenenbaum(2009)是较早的提出使用贝叶斯聚类网络对关系进行因式分解表达，他们的方法对于每一个实体都使用了超过一个向量进行表达\cite{SS09}\cite{S11}，不过Usunier等人认为对于每个实体都使用多个向量表达难以做到一般化表达。实际上在Bordes随后进行的实验也发现，这种方法构建出来的模型无法轻松地捕获处于稀疏位置的实体\cite{BordesUGWY13}。之后又有多项工作针对性地提高这类知识库模型的性能表现，但是大多数情况下提升有限，或者是应用场景狭窄，无法做到一般化。在自然语言处理领域，嵌入的概念最早由Bengio等人提出，在Bengio等人构建的语言框架模型中所有的单词都会被学习出一个嵌入。随后，Bordes提出了一种新的神经网络架构，这种架构被设计成可以将所有实体和关系嵌入到一个灵活且连续的向量空间。但由于嵌入方式的选择问题，导致构建出的模型性能较为低下。因此在2013年，Bordes根据词向量的特性，将知识库中实体的关系翻译成向量中的平移操作，从而提出了用于将实体嵌入到向量空间的翻译模型TransE\cite{BordesUGWY13}。TransE相比之前的方法，在不仅模型简单，性能提升幅度大，更为关键的是它提出了一种新的思路，给向量模型的构建提出了新的方向。之后的知识表示学习的模型，大多数都是从TransE扩展而来。
\subsection{本体与溯因诊断研究现状}
	利用本体对知识库建模是语义网领域一直备受关注的研究方向。本体的构建方法多样而且复杂，图1.1\cite{OntS01}展示了经典的本体构建流程，在构建本体的过程中，本体与观察值不一致或本体无法蕴含观察值的现象是很常见的\cite{LL13,LDI12}。因此在年来本体的研究热点开始转移到对本体的修复上。溯因推理由于推理方式与人的思考方式具有较高的一致性， 因此溯因推理技术被大量应用在本体的修复任务中。

### 2017-04-06 chap3.tex
...

	通过使用$\subseteq_\mathsf{ds}$-$\emph{minimal}$，我们获得了比子集最小更强的对解释的限制能力。因此，结合上文提到的限制条件，我们得到一类新的解释集合，称为基于决断集模板的解释，定义如下：
	\begin{definition}[基于决断集模版的解释)]
    对于一个给定的一致本体$\mathcal{O}$，一个基于$r_o(X,Y)$的模版$\mathcal{P}$以及一个观察值$\alpha$其中$\mathcal{T} \not \models \alpha$且$\mathcal{O}\cup \{\alpha\}$是一致的，对于$\alpha$在$\mathcal{O}$ 的解释$\mathcal{E}$会被称为基于决断集模版的解释，如果这个解释满足以下四个条件：
    \begin{itemize}
        \item (非平凡) $\mathcal{E} \nvDash \alpha$
        \item (一致) $\mathcal{O}\cup\mathcal{E}$ 是一致的
        \item ($\subseteq_\mathsf{ds}-\emph{minimal}$) 不存在一个对于$alpha$在$\mathcal{O}$中的解释$\mathcal{E}'$使得$\mathcal{E}'\subseteq_\mathsf{ds}\mathcal{E}$ 且$\mathcal{E}\not\subseteq_\mathsf{ds}\mathcal{E}'$。
        \item (可容许) 存在一个决断集模版$\mathcal{J}_p \in \mathcal{P}$以及$\mathcal{J}_p$的一个差异化替换$\theta$使得$\alpha = r_o(X\theta, Y\theta)$，$\mathcal{E} \subseteq \mathcal{J}_p\theta$且$\mathcal{J}_p\theta \in Jst(\alpha, \mathcal{O}\cup\mathcal{E})$
    \end{itemize}
\end{definition}

@@

>>>>

	通过使用$\subseteq_\mathsf{ds}$-$\emph{minimal}$，我们获得了比子集最小更强的对解释的限制能力。因此，结合上文提到的限制条件，我们得到一类新的解释集合，称为基于决断集模板的解释，定义如下：
	\begin{definition}[基于决断集模版的解释)]
    对于一个给定的一致本体$\mathcal{O}$，一个基于$r_o(X,Y)$的模版$\mathcal{P}$以及一个观察值$\alpha$其中$\mathcal{T} \not \models \alpha$且$\mathcal{O}\cup \{\alpha\}$是一致的，对于$\alpha$在$\mathcal{O}$ 的解释$\mathcal{E}$会被称为基于决断集模版的解释，如果这个解释满足以下四个条件：
    \begin{itemize}
        \item (非平凡) $\mathcal{E} \nvDash \alpha$
        \item (一致) $\mathcal{O}\cup\mathcal{E}$ 是一致的
        \item ($\subseteq_\mathsf{ds}-\emph{minimal}$) 不存在一个对于$\alpha$在$\mathcal{O}$中的解释$\mathcal{E}'$使得$\mathcal{E}'\subseteq_\mathsf{ds}\mathcal{E}$ 且$\mathcal{E}\not\subseteq_\mathsf{ds}\mathcal{E}'$。
        \item (可容许) 存在一个决断集模版$\mathcal{J}_p \in \mathcal{P}$以及$\mathcal{J}_p$的一个差异化替换$\theta$使得$\alpha = r_o(X\theta, Y\theta)$，$\mathcal{E} \subseteq \mathcal{J}_p\theta$且$\mathcal{J}_p\theta \in Jst(\alpha, \mathcal{O}\cup\mathcal{E})$
    \end{itemize}
\end{definition}

@@

\section{本章小结}
		在本章中，我们首先对求解的问题进行了定义，针对待求解的问题我们首先提出了变量公理的概念。在介绍了决断集后，我们结合变量公理对决断集模版进行了定义。为了限制对解释空间进行限制，我们提出了$\subseteq_\mathsf{ds}$-$\emph{minimal}$概念，并证明了$\subseteq_\mathsf{ds}$-$\emph{minimal}$的性质比$subset$-$minimal$更强。$\subseteq_\mathsf{ds}$-$\emph{minimal}$的解释不仅满足了最小解的限制，还可以对解释集中的语义等价解进行表达，从而减少了需要计算的解释数量。

			我们提出基于决断集模版的目的，就是利用决断集模版生成符合语义逻辑的最小解释。通过对决断集模版进行$(\mathcal{J}_1, \mathcal{J}_2)$ 划分，我们在知识库中寻找匹配的三元组(如果存在)计算替换$\theta$，然后利用替换$\theta$计算解释。最后，我们展示了针对问题$\Delta_p$和观察值$\alpha$进行解释集求解的完整算法。

### 2017-04-06 public.tex
...

\renewcommand{\labelenumi}{[\arabic{enumi}].}
\begin{enumerate}
\item Jianmin Ji, Hai Wan, \textbf{Peng Xiao}. On Elementary Loops and Proper Loops for Disjunctive Logic Programs [C].//
Proceedings of the 29th AAAI Conference on Artificial
Intelligence (AAAI-15). 2015.
\item Jianmin Ji, Hai Wan, \textbf{Peng Xiao}, Ziwei Huo, Zhanhao Xiao. Elementary Loops Revisited [C].//
      Proceedings of the 28th AAAI Conference on Artificial
      Intelligence (AAAI-14). 2014.
\end{enumerate}

>>>>

\renewcommand{\labelenumi}{[\arabic{enumi}].}
\begin{enumerate}
\item 	Jianfeng Du, Hai Wan, \textbf{Huaguan Ma}. Practical TBox Abduction Based on Justification Patterns [C].//
Proceedings of the 31th AAAI Conference on Artificial
Intelligence (AAAI-17). 2017.
\end{enumerate}
